### 2023-11-10 main.tex
^'

The aim of this section is studying some property of the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 

@@

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (that it is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}. The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space

@@

		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=b_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\

@@

In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality}). The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles. The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\bm{\epsilon}=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\bm{\epsilon}$. 

@@

We introduce the reversible measure \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond
	\nu_{TH}(\bm{r}|\bm{\epsilon}):&=\mathbb{P}\left(n^{x}=\bm{r}|\eta^{x}+n^{x+1}=\bm{\epsilon}\right)

@@

@@

\nu_{TH}(\bm{r}|\bm{\epsilon})&=\frac{\mathbb{P}\left(\left\{n^{x}=\bm{r}\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\bm{\epsilon}\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}=\frac{\mathbb{P}\left(n^{x}=\bm{r}\right)\,\mathbb{P}\left(n^{x+1}=\bm{\epsilon}-\bm{r}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}

@@

	\nu_{TH}(\bm{r}|\bm{\epsilon})=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}

@@

	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}
provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 

@@

	\left\{f(n^{1},\ldots,n^{x-1},\bm{r},n^{x}+n^{x+1}-\bm{r},n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})

@@

		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&

@@

		\mathcal{L}_{\text{right}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},\bm{r})-f(\bm{n})\right\}\\&
		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\beta_{k}}{\beta_{N}}\right)^{r_{k}}\left(\frac{\beta_{N}}{|\beta|}\right)^{\nu}
In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(\bm{r}|\bm{\epsilon})$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) $n^{1}$ is replaced by $\bm{r}$, according to a rate depending on the reservoirs parameters. 

@@

The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{stateSpaceDUAL-Chain}. Its generator reads

@@

where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{\text{left}}^{TH}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$ are absorbing with rate $1$

@@

i.e. they remove all dual particles at site $1$ (and $L$) and put these particles in the extra-site $0$ (and $L+1$) with rate 1. 
The duality function is the same as the original process, i.e.

@@

This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}). For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}). In view of what have been proved in the previous section of this work, some questions arise naturally:

@@

			\item Does this process shares the same $gl(N)$ Lie-algebraic structure?
	\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process?

@@

The left boundary generator reads
	\mathcal{L}_{\text{left}}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)

@@

As a consequence, we can define the boundary values in terms of the reservoir parameters as

@@

We only report the final result. The details are written in Appendix \ref{appendix-RD}. For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ reads

@@

where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{x}^{x-1}-2n_{a}^{x}$. \\For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 

@@

On the occupation variable $n_{a}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we can define the average density occupation of species $d$ at site $x$ as

@@

Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation\eqref{NSpeciesRD} where the discrete Laplacians of all species are coupled and linear reaction terms are present that we aimed for. For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question we addressed to in the beginning of this subsection.

\subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneus product measure \begin{equation}\label{reversibleMeasureRD}
	\Lambda_{rev}=\bigtimes_{x=1}^{L}\Lambda_{rev}^{x}
\end{equation}
when for any $a\in\{1,\ldots,N\}$
\begin{equation}\label{reversibilityConditionRD}
	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}
\end{equation}
This measure has marginals $\Lambda_{rev}^{x}$ given by 
\begin{equation}
	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
\end{equation}
where 
\begin{equation}
	p=p_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
\end{equation}
Namely,
\begin{equation}
	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
\end{equation}
This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries. %For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
\begin{comment}
\begin{equation}
	\begin{split}
		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
		\\
		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{g_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
		\\&
		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}+1}
	\end{split}
\end{equation}
that simplifies to

@@

The dual  process $(\bm{\xi}(t))_{t\geq 0}$ still takes values in the enlarged state space $\widetilde{\Omega}$ defined in \eqref{stateSpaceDUAL-Chain}

@@

The duality function is still given by

@@

$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the choice of the reservoirs parameters \eqref{boundaryParamRD}.

@@

	H^{rd}=H_{\text{left}}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{\text{right}}
where $\mathcal{H}_{x,x+1}$ and $H_{\text{left}},H_{\text{right}}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while

@@

Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x+1})}$ as a symmetry. \\
%\paragraph{Duality for $H_{x,x+1}^{c}$}
 We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\exp{(E^{x})}\exp{(E^{x+1})}$ with $E$ defined in \eqref{EquationEx}. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

	\\=&0

@@

where in the last equality we used the fact that map $g_{c}(\cdot)$ is surjective. \\

@@

		\Delta^{L}\mathcal{P}(1,\delta_{a}^{x})=0\\

@@

where $\Delta^{L}$ is the discrete Laplace operator on the chain of length $L$. The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{a}^{x})=1-\mathcal{P}(0,\delta_{a}^{x})$ we obtain 

@@

We consider the first addend in the curly bracket of the previous equation. We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$; we have

@@

We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ 

@@

where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 

@@

The proof is similar for $\widetilde{\mathcal{L}}_{y}^{TH}$. 

>>>>

The aim is studying some property of the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 

@@

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}. The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space

@@

		\xi_{a}^{x}=\sum_{y=1}^{L}\sum_{b=1}^{N-1}\mathbbm{1}_{\{y=x_{k}\}}\mathbbm{1}_{\{b=a_{k}\}}\qquad &\text{if}\quad x=x_{k}\;\text{and} \; a=a_{k}\\

@@

In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality,KMP}). The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles. The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\epsilon=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\epsilon$. 

@@

We introduce the reversible measure \eqref{reversibleMeasure} conditioned on the conservation of the particles on that bond
	\nu_{TH}(r|\epsilon):&=\mathbb{P}\left(n^{x}=r|n^{x}+n^{x+1}=\epsilon\right)

@@

	\end{split}\dt
Here $r=(r_{1},\ldots,r_{N})$ and  $\epsilon=(\epsilon_{1},\ldots,\epsilon_{N})$ such that $\forall a\in\{1,\ldots,N\}$  $r_{a}\in \{1,\ldots,\nu\}$ and $\epsilon_{a}\in \{0,\ldots,2\nu\}$, under the constraints 

@@

\nu_{TH}(r|\epsilon)&=\frac{\mathbb{P}\left(\left\{n^{x}=r\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\epsilon\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}=\frac{\mathbb{P}\left(n^{x}=r\right)\,\mathbb{P}\left(n^{x+1}=\epsilon-r\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\epsilon\right)}

@@

	\nu_{TH}(r|\epsilon)=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}

@@

	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}\dt
%provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 

@@

	\left\{f(n^{1},\ldots,n^{x-1},r,n^{x}+n^{x+1}-r,n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})

@@

		\mathcal{L}_{\text{left}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(r,n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&

@@

and $\mathcal{L}_{\text{right}}^{TH}$ acting similarly on the site $L$ and with parameters $\beta$'s. 
%		\mathcal{L}_{\text{right}}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(n^{1},\ldots,n^{L-1},r)-f(\bm{n})\right\}\\&
%		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\beta_{k}}{\beta_{N}}\right)^{r_{k}}\left(\frac{\beta_{N}}{|\beta|}\right)^{\nu}
In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(r|\epsilon)$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) is replaced by $r$, according to a rate depending on $r$ itself and on the reservoirs parameters. 

@@

The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads

@@

where $\mathcal{L}^{TH}_{x,x+1}$ is again \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{\text{left}}^{TH}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$ are absorbing with rate $1$:

@@

This means that they remove all dual particles at site $1$ (and $L$) and put these particles in the extra-site $0$ (and $L+1$) with rate 1. The duality function is the same as the original process, i.e.

@@

This equation is endowed with boundary conditions $\rho_{a}^{0},\rho_{\overline{a}}^{0}$ on the left and $\rho_{a}^{L+1},\rho_{\overline{a}}^{L+1}$ \\The generator of this model consists in a sum of three Markov generators: a stirring, a stirring-mutation and a pure mutation one (see section 4 of \cite{casini2022uphill}). For the lattice $\mathbb{Z}$, self-duality has been showed and the duality function is exactly \eqref{elementsABS} in case of hard-core exclusion (see section 5 of \cite{casini2022uphill}). In view of what have been proved in the previous sections of this work, some questions arise naturally:

@@

			\item Is it possible to extend the duality result to the boundary-driven case in order to have an absorbing dual process using the same $gl(N)$ Lie-algebraic structure?

@@

The left boundary generator $\mathcal{L}_{\text{left}}^{rd}$ is given by \eqref{siteGenerator} at site $1$,
%reads
%	\mathcal{L}_{\text{left}}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)

@@

As a consequence, from the above conditions we can define the boundary values in terms of the reservoir parameters as

@@

We only report the final result. The details are written in Appendix \ref{appendix-RD}. For arbitrary site $x\in \{2,\ldots,L-1\}$, the action on the occupation variable $f(\bm{n})=n_{a}^{x}$ of particle of type $a\in \{1,\ldots,N-1\}$ reads

@@

where $\Delta_{L}n_{a}^{x}= n_{a}^{x+1}+n_{a}^{x-1}-2n_{a}^{x}$. \\For $x=1$ and for all $a\in \{1,\ldots,N-1\}$ we have 

@@

On the occupation variable $n_{a}^{L}$ the action is similar, but with the upper case $1$ replaced by $L$.\\ In the spirit of \cite{casini2022uphill} we define the average density occupation of species $a$ at site $x$ as

@@

Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain the desired system of $N-1$ difference-differential equations \eqref{NSpeciesRD}. For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question we addressed to at the beginning of this subsection. 
\subsubsection{Reversible measure for the reaction-diffusion process (equilibrium)} 
The process described by the generator \eqref{RDGenerator} is reversible with respect to the homogeneous product measure \begin{equation}\label{reversibleMeasureRD}
	\Lambda_{rev}=\bigotimes_{x=1}^{L}\Lambda_{rev}^{x}
when for any $a\in\{1,\ldots,N\}$
\begin{equation}\label{reversibilityConditionRD}
	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}
This measure has marginals $\Lambda_{rev}^{x}$ given by 
	\Lambda^{x}_{rev}\sim \text{Multinomial}\left(\twoj,p_{1},\ldots,p_{N}\right)
	p=p_{a}=\frac{\alpha}{\alpha_{N}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad p_{N}=\frac{\alpha_{N}}{\alpha_{N}+(N-1)\alpha}
Namely,
	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}p^{\sum_{a=1}^{N-1}n_{a}^{x}}p^{n_{N}^{x}}
This can be proved by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundaries. %For fixed site $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the generator $\mathcal{L}_{x,x+1}^{m}$ the computation is similar and has already been proved for $\mathcal{L}_{x,x+1}$ of the multi-species stirring. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$ for arbitrary $a,b\in\{1,\ldots,N-1\}$ and $c\in\{1,\ldots,N-2\}$; the detailed balance gives
		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}\cdots \rho_{N}^{n_{N}^{x}+n_{N}^{x+1}}
		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{g_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}
		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}+1}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}+1}
that simplifies to

@@

The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space $\widetilde{\Omega}$ defined in \eqref{dualStateSpace}

@@

@@

$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{\text{left}}^{rd}$ and $\widetilde{\mathcal{L}}_{\text{right}}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}, with the specific choice of the reservoirs parameters \eqref{boundaryParamRD}. This answer to the second question addressed at the beginning of this Subsection. 

@@

	H^{rd}=H_{\text{left}}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{\text{right}}\dt
Here, $\mathcal{H}_{x,x+1}$ and $H_{\text{left}},H_{\text{right}}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while

@@

Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ commute with $\exp{(E^{x})}\exp{(E^{x+1})}$, where $E$ is defined in \eqref{EquationEx}. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

	\\=&0\dt

@@

In the last equality we used the fact that map $g_{c}(\cdot)$ is surjective. \\

@@

		\Delta_{L}\mathcal{P}(1,\delta_{a}^{x})=0\\

@@

where $\Delta_{L}$ is the discrete Laplace operator on the chain of length $L$. The equations \eqref{gamblers-ruin} can be solved and using $\mathcal{P}(1,\delta_{a}^{x})=1-\mathcal{P}(0,\delta_{a}^{x})$ we obtain 

@@

We consider the first addend in the curly bracket of the previous equation. We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$. As a result, we have

@@

We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and we obtain

@@

where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we have that

@@

The proof is similar for $\widetilde{\mathcal{L}}_{\text{right}}^{TH}$. 
